Verification of the CVM algorithm with a New Recursive Analysis Technique

### 2025-02-18 paper/sec/related_work.tex
Paper: Fix inaccuracy in related work section.

The aforementioned hash based algorithms are not unbiased.
%TODO: is there a typo? does this mean bounds on the deviation from the mean?
Flajolet et al.~\cite{flajolet1985} points it out and provides bounds on the bound.
Most authors do not discuss the matter.
It, however, is not hard to see that they are not.
One issue, for example, is that the usual method to amplify the accuracy of these algorithms is using the median, which does not preserve expectations.
In the context of query processing unbiasedness has been discussed~\cite[Section 2.1]{haas1995}, but we could not find any similar discussion for the distinct elements in the streaming model.

>>>>

The aforementioned hash based algorithms are not unbiased.
Flajolet et al.~\cite{flajolet1985} points it out and provides bounds on the distance between the expected result and the cardinality of the stream.
Most authors do not discuss the matter.
It, however, is not hard to see that they are not.
One issue, for example, is that the usual method to amplify the accuracy of these algorithms is using the median, which does not preserve expectations.
In the context of query processing unbiasedness has been discussed~\cite[Section 2.1]{haas1995}, but we could not find any similar discussion for the distinct elements problem in the streaming model.
